### 2021-11-23 README.Rmd
Improved do_condition and simplified optimization of AvRec. No EWN.

>>>>

* 2021-11-23 aMSE 0.0.0.1 Added functions to simplify the optimization of AvRec relative to the CPUE data after initial parameter estimation for each SAU using the sizemod package. Also added a comparison of size-composition data to the do_condition function. Next step will be to include the optimization of the recdevs using both CPUE and size-comp data.
